% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{graphicx}
\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{url}
\usepackage[utf8]{inputenc}

\setcounter{tocdepth}{2}
%
\begin{document}
\frontmatter
\pagestyle{headings}  % switches on printing of running heads

\addtocmark[2]{Sistemas de Recuperación de Información\\ Trabajo Final}
\mainmatter              % start of the contributions
%
\title{Sistemas de Recuperación de Información\\ Trabajo Final}
%
\titlerunning{Sistemas de Recuperación de Información\\ Trabajo Final}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Jorge J. Morgado Vega\inst{1} \and Roberto García Rodrígez\inst{1}}
%
% \authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Jorge J. Morgado Vega y Roberto García Rodrígez}
%
\institute{Universidad de la Habana, La Habana, Cuba}

\maketitle              % typeset the title of the contribution

\renewcommand\abstractname{Resúmen.}
\renewcommand\keywordname{{\bf Palabras Claves:}}
\begin{abstract}
	La recuperación de información ha sido desde sus inicios una de las tareas
	más arduas en el campo de las ciencias de la computación. Específicamente,
	la recuperación de texto es uno de los subcampos más analizados de esta área.
	El siguiente proyecto propone un sistema de recuperación de texto basado
	en modelos vectoriales. Ofrece, además un sistema de evaluación de los mismos
	sobre varias colecciones reconocidas, así como dos aplicaciones que facilitan
	la interacción del usuario con el sistema.
\keywords{recuperación de información, recuperación de texto, modelos vectoriales}
\end{abstract}
\renewcommand\abstractname{Abstract.}
\renewcommand\keywordname{{\bf Keywords:}}
\begin{abstract}
	Information retrieval has been one of the most arduous tasks in the field
	of computer science since its inception. Specifically, text retrieval is
	one of the most analyzed subfields in this area. The following project
	proposes a text retrieval system based on vector models. It also offers an
	evaluation system of the same on various recognized collections, as well as
	two applications that facilitate user interaction with the system.
\keywords{information retrieval, text retrieval, vector models}
\end{abstract}
%

\tableofcontents
\clearpage

\input{intro.tex}

\newpage

\input{desing.tex}

\input{evaluation.tex}

\input{pros_cons.tex}

\newpage

\input{conclusion.tex}

\newpage

\input{recomendation.tex}

\newpage


%
% ---- Bibliography ----
%
\begin{thebibliography}{}
%

\bibitem{ramos}
Ramos, J. (2003, December). Using tf-idf to determine word relevance in
document queries. In Proceedings of the first instructional conference on
machine learning (Vol. 242, No. 1, pp. 29-48).

\bibitem{aparicio}
Aparicio, C. F. (2021). Conferencias de Sistemas de Información. La Habana.

\bibitem{mishra}
Mishra, A., \& Vishwakarma, S. (2015, December). Analysis of tf-idf model and
its variant for document retrieval. In 2015 international conference on
computational intelligence and communication networks (cicn) (pp. 772-776). IEEE.

\bibitem{manning}
Manning, C. D. (2009). An Introduction to Information Retrieval. Cambridge UP.

\bibitem{aizawa}
Aizawa, A. (2003). An information-theoretic perspective of tf–idf measures.
Information Processing \& Management, 39(1), 45-65.

\bibitem{ellis}
Ellis, D. (1989). A behavioural approach to information retrieval system
design. Journal of documentation.

\bibitem{chowdhury}
Chowdhury, G. G. (2010). Introduction to modern information retrieval.
Facet publishing.

\bibitem{paik}
Paik, J. H. (2013, July). A novel TF-IDF weighting scheme for effective
ranking. In Proceedings of the 36th international ACM SIGIR conference on
Research and development in information retrieval (pp. 343-352).

\bibitem{baeza}
Baeza-Yates, R. a. (s.f.). Information Retrieval: Data Structures \&
Algorithms.

\bibitem{ceri}
Ceri, S., Bozzon, A., Brambilla, M., Della Valle, E., Fraternali, P., \&
Quarteroni, S. (2013). An introduction to information retrieval. In Web
information retrieval (pp. 3-11). Springer, Berlin, Heidelberg.

\bibitem{piwowarski} Piwowarski, B., Frommholz, I., Lalmas, M., \& Van
Rijsbergen, K. (2010, October). What can quantum theory bring to information
retrieval. In Proceedings of the 19th ACM international conference on
Information and knowledge management (pp. 59-68).

\bibitem{blair} Blair, D. C., \& Maron, M. E. (1990). Full-text information
retrieval: Further analysis and clarification. Information Processing \&
Management, 26(3), 437-447.

\bibitem{boyce} Boyce, B. R., Boyce, B. R., Meadow, C. T., Kraft, D. H., Kraft, D.
H., \& Meadow, C. T. (2017). Text information retrieval systems. Elsevier.

\end{thebibliography}
\clearpage
\addtocmark[2]{Subject Index} % additional numbered TOC entry
\markboth{Subject Index}{Subject Index}
\renewcommand{\indexname}{Subject Index}
\input{subjidx.tex}
\end{document}
\input{subjidx.tex}
\end{document}
